Fast Neural Machine Translation Implementation

### 2018-05-24 wnmt.2018/wnmt.tex
bah

@@

>>>>

% declaration of the new block
\algblock{ParFor}{EndParFor}
% customising the new block
\algnewcommand\algorithmicparfor{\textbf{parfor}}
\algnewcommand\algorithmicpardo{\textbf{do}}
\algnewcommand\algorithmicendparfor{\textbf{end\ parfor}}
\algrenewtext{ParFor}[1]{\algorithmicparfor\ #1\ \algorithmicpardo}
\algrenewtext{EndParFor}{\algorithmicendparfor}

@@

Since we are working on GPU optimization, it is essential to make full use of the many GPU cores available. This is accomplished by well-known parallelization methods which multi-thread the algorithms. For example, Algorithm~\ref{algo:Argmax only} is parallelized by sharding the vector $p$ and calculating $best$ and $max$ on each shard in parallel. The ultimate $best$ is found in the following reduction step, Algorithm~\ref{algo:Parallel Argmax only}.

\Comment{parallelize}
\State Create shards ${p^1...p^n}$ from $p$
\ParFor{$p^j \in {p^1...p^n}$}
  \State $max^j \gets - \infty$ 
  \ForAll{$p_i^j$ in $p^j$}
    \If{$p_i^j + b_i > max$}
      \State $max^j \gets p_i^j + b_i$
      \State $best^j \gets i$
    \EndIf
  \EndFor

\EndParFor

\Comment{reduce}
\State $max \gets - \infty$ 
\ForAll{$max^j \in max^1...max^n$}
  \If{$max^j > max$}
    \State $max \gets max^j$
    \State $best \gets best^j$
  \EndIf
\EndFor

\end{algorithmic}
\caption{Parallel find 1-best only}
\label{algo:Parallel Argmax only}
\end{algorithm}
